### 2013-02-22 doc/notes.tex
version 1 of RVD2.6 is working now.

\usepackage{algorithm2e}

@@

\begin{algorithm}[H]
\SetAlgoLined
\KwData{Counts $r_{ij}$ for experimental replicate $i$ at genomic location $j$}
\KwResult{MLE estimates for hyper-parameters $\hat{a}$ and $\hat{b}$. Samples from joint posterior distribution $p(\theta_{ij}, \alpha_j | r_{ij}; \hat{a}, \hat{b})$ for $i=1,\ldots,N$ and $j=1,\ldots,M$}
Initialize $a$ and $b$\;
\Repeat {convergence} {
	Sample $\alpha_j$ from $p(\alpha_j | a, b, \theta_{1j}, \ldots, \theta_{Nj})$ using M-H\;
	Sample $\theta_{ij}$ from $p(\theta_{ij} | \alpha_j, r_{ij})$ using Gibbs\;
	Compute MLE $\hat{a}$ and $\hat{b}$
}
\caption{Metropolis-within-Gibbs Sampling for RVD2.3 Model}
\end{algorithm}

@@

The Gamma distribution is not conjugate to the Dirichelt, so we draw samples from $p(\alpha_j | a, b, \theta_{1j}, \ldots, \theta_{Nj})$ by Metropolis-Hastings. We use a proposal distribution,
\begin{equation}
	\alpha_j^{k \text{(new)}} | \alpha_j^k \thicksim \text{Gaussian}(\alpha_j^k, 0.05),
\end{equation}
which we find mixes sufficiently fast to sample from the posterior after a burn-in of length X.

>>>>

\usepackage[boxed]{algorithm2e}

@@

\begin{algorithm}[H]
\SetAlgoLined
\KwData{Counts $r_{ij}$ for experimental replicate $i$ at genomic location $j$}
\KwResult{MLE estimates for hyper-parameters $\hat{a}$ and $\hat{b}$. Samples from joint posterior distribution $p(\theta_{ij}, \alpha_j | r_{ij}; \hat{a}, \hat{b})$ for $i=1,\ldots,N$ and $j=1,\ldots,M$}
Initialize $a$ and $b$\;
\Repeat {convergence} {
	Sample $\alpha_j$ from $p(\alpha_j | a, b, \theta_{1j}, \ldots, \theta_{Nj})$ using Metropolis-Hastings\;
	Sample $\theta_{ij}$ from $p(\theta_{ij} | \alpha_j, r_{ij})$\;
	Compute maximum-likelihood estimates $\hat{a}$ and $\hat{b}$
}
\caption{Metropolis-within-Gibbs Sampling for RVD2.3 Model}
\end{algorithm}

@@

The Gamma distribution is not conjugate to the Dirichlet, so we draw samples from $p(\alpha_j | a, b, \theta_{1j}, \ldots, \theta_{Nj})$ by Metropolis-Hastings. We use a proposal distribution,
\begin{equation}
	\alpha_j^{k \text{(new)}} | \alpha_j^k \thicksim \text{Gaussian}(\alpha_j^k, 0.05),
\end{equation}
which we find mixes sufficiently fast to sample from the posterior after a burn-in of length X.
